### 2022-10-06 chapters/introduction.tex
update : introduction

The best way to do so is to formulate a theory behind the energy consumption of algorithms, such as the complexity and the o notation.
Unfortunately, this is not possible in the current state of the art. due to the lack of knowledge about the energy consumption of the algorithms, and the strong correlation between this consumption and the hardware configuration.
Unlike algorithm optimization in the field of performance, which is agnostic toward the platform, the energy consumption of the algorithms is dependent on the execution environment.
Therefore, for the moment we will start by formulating some hypotheses and explore them using empirical analysis.

\subsection*{Objectives}

% \url{https://www.statista.com/statistics/871513/worldwide-data-created/}

% https://www.iea.org/reports/data-centres-and-data-transmission-networks

>>>>

The best way to do so is to formulate a theory behind the energy consumption of algorithms, such as the complexity and the o notation.
Unfortunately, this is not possible in the current state of the art. Due to the lack of knowledge about the energy consumption of the algorithms, and the strong correlation between this consumption and the hardware configuration.
Unlike algorithm optimization in the field of performance, which is agnostic toward the platform, the energy consumption of the algorithms is dependent on the execution environment.
Therefore, for the moment we will start by formulating some hypotheses and explore them using empirical analysis.
Figure~\ref{fig:thesis_position} highlights this thesis's position on the sustainability of ICT; while this thesis only addresses a small portion of ICT's energy usage, we feel it is a step in the right direction for additional solutions to mature in order to preserve humanity.

\subsection*{Objectives}
As seen in  our thesis is positioned in the brick of software optimization in the field of energy consumption. 
Our main objective is to reduce the energy consumption using 
% \url{https://www.statista.com/statistics/871513/worldwide-data-created/}
% https://www.iea.org/reports/data-centres-and-data-transmission-networks
